---
title: "stats_camila"
author: "cvt"
date: "3/18/2020"
output: html_notebook
---

##  Code stats descriptives
1. load data
change workdirectory and load dataset after cleaning

```{r}
path = "~/Documents/3eme-annee/Data R/Projet_Sante-/"
setwd(path)
load("dataset.Rdata")
str(data)
```

2. Description
In order to analyze the dataset, we change onehotencoding to factor. Then, some columns are not necessary (case_num and onehotencoding) so they become null. 

To factor : 'prod1' and 'prod2' are codes from products that means they are categorical data (tofactor)
```{r}
#data[6:31] 
## Onehot Encoding to factor
data.stats <- data
data.stats$output <- (substring(names(data[,6:31]),first = 11)[max.col(data[,6:31])])
data.stats[,6:31] <- NULL
data.stats$case_num <- NULL
data.stats$output <- as.factor(data.stats$output)
#products as factor
data.stats$prod1 <- as.factor(data.stats$prod1)
data.stats$prod2 <- as.factor(data.stats$prod2)
```

3. Numerical 
```{r}
num <- Filter(is.numeric, data.stats)
print(names(num))
boxplot(num)
```
### C'est quoi `psu` et `weight` ?
```{r}
summary(num)

```
```{r}
library("ggplot2")
get.table.freq <- function(x) {
                #cut variable in groups using Sturges's rule
                factorx <- factor(cut(x, breaks=nclass.Sturges(x)))
                xout <- as.data.frame(table(factorx))
                #Add cumFreq and proportions
                xout <- transform(xout, cumFreq = cumsum(Freq), relative = prop.table(Freq))
}
age <- get.table.freq(data.stats$age)
psu <- get.table.freq(data.stats$psu)
weight <- get.table.freq(data.stats$weight)

ggplot(data =  age, aes(x = factorx, y = relative))+
  geom_bar(stat="identity")
ggplot(data =  psu, aes(x = factorx, y = relative))+
  geom_bar(stat="identity")
ggplot(data =  weight, aes(x = factorx, y = relative))+
  geom_bar(stat="identity")
```

4. Categorical data (factor)
```{r}
summary( Filter(is.factor, data.stats))
print(str(Filter(is.factor, data.stats)))
```

```{r}
get_proportion <- function(x) {
                #as.data.frame(prop.table(sort(table(x),decreasing = TRUE)))
                as.data.frame((sort(table(x),decreasing = TRUE)))
}
plot(get_proportion(data.stats$output))
print(get_proportion(data.stats$output))
```
## on a fait un merge entre diag et diag autre. Est-ce un bon choix ?
```{r}
str(data.stats$diag)
print(unique(data.stats$diag))
print(get_proportion(data.stats$diag))
```

- Prod1

```{r}
str(data.stats$prod1)
print(get_proportion(data.stats$prod1))
#on laisse les codes?
```
5. 
```{r}
str(data.stats$prod2)
print(get_proportion(data.stats$prod2))

```
```{r}

```


Graphics contigence tables
```{r}
library(ggplot2)
#install.packages("ggpubr")
library(ggpubr)
#analyse location and output
cont.table.loc <- as.data.frame(prop.table(table(data.stats$location,data.stats$output)))
cont.table.sex <- as.data.frame(prop.table(table(data.stats$sex,data.stats$output)))
cont.table.race <- as.data.frame(prop.table(table(data.stats$race,data.stats$output)))
par(mfrow = c(3,1))
ggballoonplot(cont.table.loc, fill = "value")+
  scale_fill_viridis_c(option = "C")
ggballoonplot(cont.table.sex, fill = "value")+
  scale_fill_viridis_c(option = "C")
ggballoonplot(cont.table.race, fill = "value")+
  scale_fill_viridis_c(option = "C")

```
# Component analysis
```{r}

library(FactoMineR)
library(factoextra)
#other
par(mfrow =c(3,1))

cont.table.loc <- ((table(data.stats$location,data.stats$output)))
res.ca <- CA(cont.table.loc, graph = FALSE)
fviz_ca_biplot(res.ca, repel = TRUE, title = "CA location and output")

cont.table.str <- ((table(data.stats$stratum,data.stats$output)))
res.ca <- CA(cont.table.str, graph = FALSE)
fviz_ca_biplot(res.ca, repel = TRUE, title = "CA stratum and output")

```
```{r}


```


```{r}
#cross the time
months <- format(data.stats$trmt_date, "%Y-%m")
age.mean <- aggregate(data.stats["age"],by=list(months), mean)
age.min <- aggregate(data.stats["age"],by=list(months), min)
age.max <- aggregate(data.stats["age"],by=list(months), max)


plot(age.mean[,2],type="l", ylim = c(0,150),xlab = "")
lines(age.max[,2],col = "dark red")
lines(age.min[,2],col = "dark blue")
axis(3, at= seq(1,60,10),labels= age.mean[seq(1,60,10),1])
```

