---
title: "stats_camila"
author: "cvt"
date: "3/18/2020"
output: html_document
---

##  Code stats descriptives
1. load data
change workdirectory and load dataset after cleaning

```{r}
path = "~/Documents/3eme-annee/Data R/Projet_Sante-/"
setwd(path)
load("dataset.Rdata")
str(data)
```

2. Description
In order to analyze the dataset, we change onehotencoding to factor. Then, some columns are not necessary (case_num and onehotencoding) so they become null. 

To factor : 'prod1' and 'prod2' are codes from products that means they are categorical data (tofactor)
```{r}
#data[6:31] 
## Onehot Encoding to factor
data.stats <- data
data.stats$output <- (substring(names(data[,6:31]),first = 11)[max.col(data[,6:31])])
data.stats[,6:31] <- NULL
data.stats$case_num <- NULL
data.stats$output <- as.factor(data.stats$output)
#products as factor
data.stats$prod1 <- as.factor(data.stats$prod1)
data.stats$prod2 <- as.factor(data.stats$prod2)
```

3. Numerical 
```{r}
num <- Filter(is.numeric, data.stats)
print(names(num))


boxplot(num)
```
### C'est quoi `psu` et `weight` ?
```{r}
summary(num)
```

4. Categorical data (factor)
```{r}
plot(sort(table(data.stats$output),decreasing = TRUE))
```



```{r}
toFrequence <- function(x) {
        as.data.frame(sort(table(x),decreasing = TRUE))
}
fac <- Filter(is.factor, data.stats)
summary(fac)
```
Graphics contigence tables
```{r}
library(ggplot2)
#install.packages("ggpubr")
library(ggpubr)
#analyse location and output
cont.table.loc <- as.data.frame(prop.table(table(data.stats$location,data.stats$output)))
cont.table.sex <- as.data.frame(prop.table(table(data.stats$sex,data.stats$output)))
cont.table.race <- as.data.frame(prop.table(table(data.stats$race,data.stats$output)))
par(mfrow = c(3,1))
ggballoonplot(cont.table.loc, fill = "value")+
  scale_fill_viridis_c(option = "C")
ggballoonplot(cont.table.sex, fill = "value")+
  scale_fill_viridis_c(option = "C")
ggballoonplot(cont.table.race, fill = "value")+
  scale_fill_viridis_c(option = "C")

```
# Component analysis
```{r}

library(FactoMineR)
library(factoextra)
#other
par(mfrow =c(3,1))

cont.table.loc <- ((table(data.stats$location,data.stats$output)))
res.ca <- CA(cont.table.loc, graph = FALSE)
fviz_ca_biplot(res.ca, repel = TRUE, title = "CA location and output")

cont.table.str <- ((table(data.stats$stratum,data.stats$output)))
res.ca <- CA(cont.table.str, graph = FALSE)
fviz_ca_biplot(res.ca, repel = TRUE, title = "CA stratum and output")

```


```{r}
#cross the time
months <- format(data.stats$trmt_date, "%Y-%m")
age.mean <- aggregate(data.stats["age"],by=list(months), mean)
age.min <- aggregate(data.stats["age"],by=list(months), min)
age.max <- aggregate(data.stats["age"],by=list(months), max)


plot(age.mean[,2],type="l", ylim = c(0,150),xlab = "")
lines(age.max[,2],col = "dark red")
lines(age.min[,2],col = "dark blue")
axis(3, at= seq(1,60,10),labels= age.mean[seq(1,60,10),1])
```

